Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-08-18 psy_peds.Rmd
weekly count for distinct diseaasee groups distinct than mental

>>>>

patient_count_per_week_byCategory %>%
  filter( icd_description_category %in% c("Neoplams","Diseases of the respiratory system", "Diseases of the nervous system", "Diseases of the digestive system", "Diseases of the blood", "Congenital malformations, deformations and chromosomal abnormalities" )) %>%
  ggplot(aes(weeks, n, color = factor(icd_description_category))) +
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  geom_point() + 
  theme(axis.text.x = element_text(angle=45, vjust = 1, hjust=1), legend.position = "none" ) +
  labs(title = "Weekly patient counts",
       subtitle = "(by ICD category)",
       y = "Counts", x = "Calendar weeks") + 
  facet_wrap(~ icd_description_category)

ggsave("output/overall_weekly_count_all_comparison_other_categories_facet_wrap.png", width = 18, height = 9, units="cm")
